Capstone Movielens Report

### 2025-05-28 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
loess function draft description.

@@

This is a helper function that calculates the _UMGYD effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGYD_effect](#func.train_UMGYD_effect)) described below.

@@

The following is the source code of the function:
```{r eval=FALSE}
calc_UMGYD_effect <- function(date_general_effect){
  date_general_effect |>
    group_by(year) |>
    summarise(ye = mean(de, na.rm = TRUE))
}
```

@@

This function is used to train the current model using the _Train Set_ dataset passed in the `train_set` parameter.
The following is the source code of the function:
```{r eval=FALSE}
train_UMGYD_effect <- function(train_set, lambda = 0){
  if (is.na(lambda)) {
    stop("Function: train_UMGYD_effect
`lambda` is `NA`")
  }

  train_set |>
    calc_day_general_effect(lambda) |>
    calc_UMGYD_effect()
}

>>>>

#### [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) Function {#func.loess_de}
\

This is a helper function that calculates the _Smoothed Day Effect_ of user ratings and is intended to be used in other functions and scripts (such as [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect)) described below.

###### ***de_bias.dat***
\
The _day general effect_ data, which is a data structure returned by any of the following functions described above:

###### ***degree***
\

###### ***span***
\

##### Details
\

The function is a wrapper to the [stats::loess] and calls it under the hood.

The following is the source code of the function:
```{r eval=FALSE}
loess_de <- function(de_bias.dat, degree = NA, span = NA){
  if(is.na(degree)) degree = 2
  if(is.na(span)) span = 0.75
  loess(de ~ days, span = span, degree = degree, data = de_bias.dat)
}
```

::: {.noteblock data-latex=""}
The source code of the [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) script on _GitHub_.
:::

@@

This is a helper function that calculates the _UMGYD Effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGYD_effect](#func.train_UMGYD_effect)) described below.

@@

The following is the source code of the function:
```{r eval=FALSE}

@@

This function is used to train the current model using the _Train Set_ dataset passed in the `train_set` parameter.
The following is the source code of the function:
```{r eval=FALSE}
